---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## PRODUCING OF THREE BAR PLOTS 

&nbsp;&nbsp;

### PLOT  ( 1 )


**Here I am displaying Bar Plot of the mean value from the given total subscribers inputs, divided by each of the given YouTube categories. Each category filled by a  different colour **

&nbsp;

```{r, echo = FALSE}

library(tidyverse)


logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRUv7cL5VGV613KuJqOcl-UlJ_NGABdo2D939DrGecYDMq6Ehe-3quxm9pkQhncro2IScRsfj1esVRx/pub?gid=142813942&single=true&output=csv")

latest_data <- (logged_data) %>%
  rename(All_YouTube_category_Inputs = 16,
         Total_Subscribers = 17,
         Total_Views = 18)

mean_values_total_subscribers <- latest_data %>%
  group_by(All_YouTube_category_Inputs) %>%
  summarize(mean_value = mean(Total_Subscribers, na.rm = TRUE))




mean_values_total_subscribers_bar_plot <- ggplot(mean_values_total_subscribers, aes(x = All_YouTube_category_Inputs, y = mean_value, fill = All_YouTube_category_Inputs)) +
  geom_col() +
  labs(title = "Mean Total Subscribers Value by Category",
       x = "YouTube Category Inputs",
       y = "Mean Value in Millions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2")


mean_values_total_subscribers_bar_plot



highest_max_subscribers <- mean_values_total_subscribers %>%
  filter(mean_value == max(mean_value))


ROUNDED_SUBSCRIBERS_VALUE <- round(highest_max_subscribers $ mean_value, 2)
 


```


The highest value mean by the category is '`r highest_max_subscribers$All_YouTube_category_Inputs`' with value of `r ROUNDED_SUBSCRIBERS_VALUE` Million!.





&nbsp;&nbsp;&nbsp;&nbsp;


### PLOT  ( 2 )


**Here I am displaying Bar Plot of the MAX Value from the given total views inputs, divided by each of the given YouTube categories. Each category filled by a  different colour **

&nbsp;

```{r, echo = FALSE}

max_values_total_views <- latest_data %>%
  group_by(All_YouTube_category_Inputs) %>%
  summarize(max_value = max(Total_Views, na.rm = TRUE))


max_values_total_viewers_bar_plot <- ggplot(max_values_total_views, aes(x = All_YouTube_category_Inputs, y = max_value, fill = All_YouTube_category_Inputs)) +
  geom_col() +
  labs(title = "Maximum Total Views Value by Category",
       x = "YouTube Category Inputs",
       y = "Maximum Value in Millions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2")

max_values_total_viewers_bar_plot


highest_from_max_views <- max_values_total_views %>%
  filter(max_value == max(max_value))



ROUNDED_TOTAL_VIEWERS_VALUE <- round(highest_from_max_views$max_value,2)



```


The highest value total views by the category is '`r highest_from_max_views$All_YouTube_category_Inputs`' with value of `r ROUNDED_TOTAL_VIEWERS_VALUE` Million!.

&nbsp;&nbsp;&nbsp;&nbsp;


### PLOT  ( 3 )


**Here I am displaying a Grouped Bar Plot of the total from the given Total Subscribers and Total Views, divided by each of the given YouTube categories. Each category filled by a  different colour. All values in Millions.**

&nbsp;

```{r, echo = FALSE}

latest_data_long_formatted <- pivot_longer(latest_data, 
                        cols = c(Total_Subscribers, Total_Views),
                        names_to = "Variable",
                        values_to = "Value")


Two_values_Grouped_Plot <- ggplot(latest_data_long_formatted, aes(x = Variable, y = Value, fill = All_YouTube_category_Inputs)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Subscribers x Views Grouped Bar Plot",
       x = "YouTube Category Inputs",
       y = "Value in Millions")


Two_values_Grouped_Plot






```







